---
title: "Air travel carbon"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dplyr.summarise.inform = FALSE)
```

```{r libraries, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(geosphere)
library(readxl)
library(janitor)
```

```{r read_data, message = FALSE}
airports <- 
  read_csv(here('ProcData', 'medlarge_airports.csv'))
OriginalLookup <- 
  read_excel(here('Data', 'OriginalLookup.xlsx'), range = "a1:j154") %>% 
  clean_names()
```

```{r get_origins}
origin <- 
  # Filter out airports not in the original lookup.
  airports %>% 
  filter(iata_code %in% OriginalLookup$city_airport_code) %>% 
  select(c('name', 'latitude_deg', 'longitude_deg', 'continent', 'iso_country', 'iso_region', 'iata_code'))
```

```{r add_destinations}
dest <- 
  # Destination airports to be included in the output
  airports %>% 
  filter(iata_code %in% c('LHR', 'BHX')) %>% 
  select(dest_iata = iata_code,
         dest_longitude = longitude_deg,
         dest_latitude = latitude_deg)

air_distances <- 
  # Repeat origin rows for each destination; add destination details.
  bind_rows(origin, origin) %>% 
  mutate(dest_iata = rep(dest$dest_iata, each = nrow(origin))) %>% 
  left_join(dest) %>% 
  # Calculate shortest distance between origin and destination
  mutate(distance = distGeo(bind_cols(longitude_deg, latitude_deg), bind_cols(dest_longitude, dest_latitude)))
```

Compare our distances with those from the original lookup.

```{r compare_distances}
combined <- 
  air_distances %>% 
  left_join(OriginalLookup, by = c('iata_code' = 'city_airport_code'))

error_lhr <- 
  combined %>% 
  filter(dest_iata == 'LHR') %>% 
  mutate(lhr_error = distance / 1000 - distance_from_lhr_km) %>% 
  select(c('country_territory', 'iata_code', 'distance_from_lhr_km', 'lhr_error'))
  
error_lhr %>% 
  arrange(desc(abs(lhr_error))) %>% 
  head()

error_bhx <- 
  combined %>% 
  filter(dest_iata == 'BHX') %>% 
  mutate(bhx_error = distance / 1000 - distance_from_bhx_km) %>% 
  select(c('country_territory', 'iata_code', 'distance_from_bhx_km', 'bhx_error'))

error_bhx %>% 
  arrange(desc(abs(bhx_error))) %>% 
  head()
```

Nothing to worry about, though it might be worth checking the entries for the top three errors.

#### Which airports on the original lookup have we missed?

```{r}
OriginalLookup %>% 
  anti_join(origin, by = c('city_airport_code' = 'iata_code'))

```

I think Berlin Tegel Airport (TXL) is now closed and the main Berlin airport should be Berlin Brandenburg (BER).

Also for noting: SKP is duplicated in the original lookup as serving both Macedonia and North Macedonia. Similarly TLV is duplicated as serving Israel and the State of Palestine.

This accounts for the difference in lengths of `origin` and `OriginalLookup`


## References

Original data from: https://ourairports.com/data/ Accesssed 2021-02-20 .



