---
title: "Estates Pre-process"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dplyr.summarise.inform = FALSE)
```

```{r libraries, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(janitor)
```

# Eda of HESA Estates data

Environmental information for UK higher education providers collected as part of the Estates management record. The data covers the academic years 2015/16 to 2018/19.

A single CSV file was downloaded on 2021-02-04 from: https://www.hesa.ac.uk/data-and-analysis/estates/environmental

```{r read_data}
# Read everything as char, except skip column 6 (Table)
estates <- 
  read_csv(here('Data', 'data.csv'), skip = 11, col_types = 'ccccc-ccc') %>% 
  clean_names()
```

Sort out non-numeric values

There appear to be two types of enty in the `value` column that can't be coerced to `numeric` by `as.numeric`.

1. Character strings from the set {'Basic', 'Medium', 'Detailed'}. These are always associated with the `category_marker` "Method of Scope 3 carbon emissions from waste". For the moment we will remove these rows and save separately.

```{r remove_Scope3Method}
scope3method <- 
  estates %>% 
  filter(category_marker == "Method of Scope 3 carbon emissions from waste")

#unique(scope3method$value)

estates <- 
  estates %>% 
  filter(category_marker != "Method of Scope 3 carbon emissions from waste")
```

2. Numbers followed by a % symbol. These are dealt with by removing the symbol, since it is included in the `category` column.

```{r remove%symbol}
estates <-
  estates %>% 
  mutate(value = str_replace(value, '%', ''))
```

We can now convert the `value` column to numeric.

```{r make_numeric_values, warning=FALSE}
estates <- 
  estates %>% 
  mutate(value = as.numeric(value))
```

```{r}
write_csv(estates, here('ProcData', 'estates.csv'))
write_csv(scope3method, here('ProcData', 'scope3method.csv'))
```




